The problem and promise of scale in multilayer animal social networks

### 2020-09-18 paper/manuscript.Rmd
cap box1

# Box 1
Social phenotype has been increasingly linked to individual fitness, including
in primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012;
@Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Social and temporal
scales have emerged as important variables for understanding the fitness
consequences of social network position [@Almeling_2016; @Berger_2015;
@Brent_2017; @Holekamp_2011].

>>>>

# Box 1: Phenotypes and Individual Fitness
Social phenotype has been increasingly linked to individual fitness, including
in primates [@Brent_2017; @Thompson_2019], dolphins [@Stanton_2012;
@Stanton_2011], and birds [@McDonald_2007; @Royle_2012]. Social and temporal
scales have emerged as important variables for understanding the fitness
consequences of social network position [@Almeling_2016; @Berger_2015;
@Brent_2017; @Holekamp_2011].
